% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jianbo Ma}

\basicInfo{
  \email{ma_jian_bo1@163.com} \textperiodcentered\ 
  \phone{(+86) 177-6711-2408} \textperiodcentered\ 
  }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Zhejiang  University (ZJU)}, Hangzhou, China}{2018.9 -- Present}
\textit{Master student} in Computer Science and Technology (CS), expected March 2021
\datedsubsection{\textbf{Jilin University}, Changchun, China}{2014 -- 2018}
\textit{B.S.} in Computer Science and Technology (CS)


\section{\faUsers\ Experience}
\datedsubsection{\textbf{Alibaba inc }}{2019.9 -- Present}
\role{Intern}
Brief introduction: Aiops in Kubernetes situation.
\begin{itemize}
  \item Test the impact of  pods and nodes on the core components of the kubernetes master with Kubemark.
  \item Use data collected by prometheus to build regression models for pod, node, and master performance.Finish config     recommendation for ACK.
  \item Design and complete large-scale cluster performance tests with SLA defined by kubernetes community.
\end{itemize}

\datedsubsection{\textbf{Google Summer of Code } Open source hangzhou, China}{2018 -- 2019}
\role{ Intern}
Brief introduction: Run GPUSharing workloads with Kubernetes+kubeflow.
\begin{itemize}
  \item Integrate MPS with GPUShare.
  \item Integrate GPUShare with arena in tensorflow-serving situation.Implement kubernetes scheduling with GPU merory but not card.
  \item Add a new feature to display GPU memory in arena.Make user better understand the usage of GPU resources.
\end{itemize}



% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: golang  > C++ > Java >python
  \item Platform: Linux、git、shell、
  \item Development: Kubernetes,docker,prometheus、tensorflow
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{2} Prize}, Award on JiLin University }{2014-2015}
\datedline{\textit{\nth{1} Prize}, Award on JiLin University }{2017-2018}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: https://sakuralbj.github.io/
  \item GitHub: https://github.com/Sakuralbj
  \item Languages: English - Fluent.
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
